---
title: "am5088_hw6"
author: "Anika Mitchell"
date: "2024-12-01"
output: html_document
---
Load libraries
```{r setup}
library(tidyverse)
library(dplyr)
library(modelr)
library(purrr)
```

Load data
```{r load cp data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities
```{r bootstrap and model}
set.seed(123)
boot_results = map(1:5000, ~{
boot_sample = weather_df %>% sample_frac(size = 1, replace = TRUE)
lm(tmax ~ tmin, data = boot_sample)
model = lm(tmax ~ tmin, data = boot_sample)
tibble(
  rsq = broom::glance(model)$r.squared,
  log_beta0_beta1 = log(broom::tidy(model)$estimate[1] * broom::tidy(model)$estimate[2])
  )
})
boot_results_df = tibble(
rsq = map_dbl(boot_results, "rsq"),
log_beta0_beta1 = map_dbl(boot_results, "log_beta0_beta1")
)
  
```

Plot distribution for R^2
```{r squared plot}
ggplot(boot_results_df, aes(x = rsq)) +
geom_histogram(bins = 50) +
theme_minimal() +
labs(title = "Distribution of R^2 (bootstrap)", x = "R^2", y = "Count")

```

Plot distribution for 
```{r log plot}
ggplot(boot_results_df, aes(x = log_beta0_beta1)) +
geom_histogram(bins = 50) +
theme_minimal() +
labs(title = "Distribution of log(β0 * β1) (bootsrap)", x = "log(β0 * β1)", y = "Count")

```

**Both distributions look pretty normal.** 
Read in data
```{r load wpost data}
wposthomicide_data = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

Data wrangling/cleaning
```{r clean up data}
cleaned_homicide_data <- wposthomicide_data |>
  mutate(
  city_state = paste(city, state, sep = ", "),
  resolved = if_else(disposition == "Closed by arrest", 1, 0),
  victim_race = factor(victim_race),
  victim_age = as.numeric(victim_age)
  ) |>
  filter(
    !city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"),
    victim_race %in% c("White", "Black")
  )
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors.

```{r glm regression}


```

