---
title: "am5088_hw6"
author: "Anika Mitchell"
date: "2024-12-01"
output: html_document
---
Load libraries
```{r setup}
library(tidyverse)
library(dplyr)
library(modelr)
library(purrr)
library(broom)
```

Load data
```{r load cp data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities
```{r bootstrap and model}
set.seed(123)
boot_results = map(1:5000, ~{
boot_sample = weather_df %>% sample_frac(size = 1, replace = TRUE)
lm(tmax ~ tmin, data = boot_sample)
model = lm(tmax ~ tmin, data = boot_sample)
tibble(
  rsq = broom::glance(model)$r.squared,
  log_beta0_beta1 = log(broom::tidy(model)$estimate[1] * broom::tidy(model)$estimate[2])
  )
})
boot_results_df = tibble(
rsq = map_dbl(boot_results, "rsq"),
log_beta0_beta1 = map_dbl(boot_results, "log_beta0_beta1")
)
  
```

Plot distribution for R^2
```{r squared plot}
ggplot(boot_results_df, aes(x = rsq)) +
geom_histogram(bins = 50) +
theme_minimal() +
labs(title = "Distribution of R^2 (bootstrap)", x = "R^2", y = "Count")

```

Plot distribution for 
```{r log plot}
ggplot(boot_results_df, aes(x = log_beta0_beta1)) +
geom_histogram(bins = 50) +
theme_minimal() +
labs(title = "Distribution of log(β0 * β1) (bootsrap)", x = "log(β0 * β1)", y = "Count")

```

**Both distributions look pretty normal.** 

##Problem 2
Read in data
```{r load wpost data}
wposthomicide_data = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

Data wrangling/cleaning
```{r clean up data}
cleaned_homicide_data <- wposthomicide_data |>
  mutate(
  city_state = paste(city, state, sep = ", "),
  resolved = if_else(disposition == "Closed by arrest", 1, 0),
  victim_race = factor(victim_race),
  victim_age = as.numeric(victim_age)) |>
  filter(
    !city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"),
    victim_race %in% c("White", "Black")
  )

cleaned_homicide_data |>
group_by(city_state) |>
filter(n() >= 10)
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors.

Log Regression: Balitomre + output with estimate and confidence intervals
```{r glm regression baltimore}
baltimore_data <- cleaned_homicide_data |>
  filter(city_state == "Baltimore, MD")

baltimore_model <- glm(
  resolved ~ victim_age + victim_sex + victim_race, 
  data = baltimore_data, 
  family = binomial()
)

baltimore_data_results <- broom::tidy(baltimore_model, conf.int = TRUE, exponentiate = TRUE) |>
filter(term == "victim_sexMale")

baltimore_data_results

```

Log Regression: All Cities
```{r glm regression all cities }
all_city_results <- cleaned_homicide_data |>
group_by(city_state) |>
nest() |>
mutate(
  model = map(data, ~glm(resolved ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
  tidy_model = map(model, ~broom::tidy(.x, conf.int = TRUE, exponentiate = TRUE))
  ) |>
  unnest(tidy_model) |>
  filter(term == "victim_sexMale")
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

Plot for ALl Cities:
```{r plot for all cities regression}
city_results_sorted <- all_city_results |>
arrange(estimate)
ggplot(city_results_sorted, aes(x = reorder(city_state, estimate), y = estimate)) +
geom_point() +
geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.5) +
coord_flip() +
theme_minimal() +
labs(
    title = "Odds Ratios by gender and city",
    x = "City",
    y = "log odds"
  ) +
scale_y_log10()
```


##Problem 3:
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

load data
```{r load in child bw data}
birthweight_data <- read_csv("/Users/anika/Desktop/building_blocks/HW6/am5088_hw6/birthweight.csv")
```

data wrangling + get rid of missing data
```{r wrangle child bw data}
cleaned_birthweight_data <- birthweight_data |>
mutate(
    malform = factor(malform, levels = c(0, 1), labels = c("Absent", "Present")),
    babysex = factor(babysex, levels = c(1, 2), labels = c("Male", "Female")),
    frace = factor(frace),
    mrace = factor(mrace)
  ) |>
  drop_na()
```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r proposed child bw regression model}

child_bw_model <- lm(bwt ~ blength + bhead + fincome + gaweeks + smoken, data = cleaned_birthweight_data)

summary(child_bw_model)

```
*the factors that my model includes are general anthropometric measurements like length, and head circumference. I also included family income, gestational age (weeks), and mother's smoking data. I expect these predictors to have a linear relationship with the outcome (ch bw). I chose not to select too many factors to try and prevent overfitting but I did want to have a mix of baby data + mom/SES data.* 

plot residuals against fitted values:
```{r residuals and fitted values plot}
birthweight_with_residuals <- cleaned_birthweight_data |>
  add_predictions(child_bw_model) |>
  add_residuals(child_bw_model)

ggplot(birthweight_with_residuals, aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_minimal() +
  labs(
    title = "Proposed Mode: Residuals against Fitted Values",
    x = "Fitted Values",
    y = "Residuals"
  )
```
My plot looks fine and nothing too out of the ordinary. There is a clear clustering around the line


Hi TA, this is a quick comment that for some reason (probably because I used an absolute path sorry), my code runs but then sometimes it then tells me that the file doesn't exist and then I go to the folder and it is deleted? Not by me, so then I redownload it in and run it and it works. I'm not sure what the reason is but it's probably the reason not to rely on absolute paths, but also I was running into errors reading in the data and on a time crunch. Just writing this here in case that causes an error too. I have screenshots of it working. Thanks! -Anika






